\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\vspace{-20pt}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/vivek-anand-jain/}{\Large Vivek Jain}} & Email:  \href{mailto:jain.vivek.anand@gmail.com}{jain.vivek.anand@gmail.com}\\
    \href{https://github.com/vivek-anand-jain/}{\faGithub \hspace{1pt} https://github.com/vivek-anand-jain}& Mobile:  +1-951-772-5682 \\
  \href{https://www.linkedin.com/in/vivek-anand-jain/}{\faLinkedin\hspace{1pt} https://www.linkedin.com/in/vivek-anand-jain/}& \textit{Networking and Systems}\\
  \href{https://vivek-anand-jain.github.io}{\faChrome \hspace{1pt} https://vivek-anand-jain.github.io} & \textit{C/C++, Java, Python, Go}
\end{tabular*}

\vspace{-10pt}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California Riverside}{Riverside, CA, USA}
      {Pursuing Ph.D. advised by Dr. K. K. Ramakrishnan; GPA: 3.95 / 4}{September 2019 - Present}
    \resumeSubheading
      {National Institute of Technology Karnataka}{Surathkal, Karnataka, India}
      {M.Tech in Computer Science and Engineering; GPA: 8.56 / 10}{Aug 2016 - June 2018}
    \resumeSubheading
      {Shri Guru Gobind Singhji Institute of Engineering and Technology }{Nanded, MH, India}
      {B.Tech in Computer Science and Engineering; GPA: 8.35 / 10}{Aug 2011 - June 2015}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{Programming Languages:}{C/C++, Python, Java, Go}

  \resumeSubItem{Domain:}{Computer Networks, Data center Networks, Cellular Networks, Operating Systems, Distributed Systems}
 
  \resumeSubItem{Technologies:}{Docker Containers, Microservices, Serverless, NOSQL, RPC, REST, Unit testing}
 
 \resumeSubItem{Framework:}{Kubernetes, Knative, Istio, Cassandra, gRPC, protobuf, Openstack, Linux device drivers, gTest}

 \resumeSubItem{Build Systems and Version control:}{Bazel, Make, waf, Git, Gerrit, Maven}

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\vspace{-5pt}
     \resumeSubheading
      {ns-3 \textit{(Open Source)}}{}
      {Active contributor for TCP module}{Dec 2017 -- Present}
      \resumeItemListStart
      % \textit{Technology stack: C++, waf}
        \resumeItem{}{Developed various AQM \& TCP model: ECN, PRR, DCTCP, BBR, PI, BLUE, SFBlue }
        \resumeItem{}{Serving as Google Code In \& Google Summer of Code mentor for the ns-3 project from last 2 years}
      \resumeItemListEnd
% \subsection*{WORK EXPERIENCE}
    \resumeSubheading{Tarana Wireless India Pvt. Ltd.}{Pune, India}
      {Network Software Engineer}{Jun 2018 -- September 2019}
      \resumeItemListStart
      %\textit{Technology stack: C++, gRPC, bazel, gTest, protobuf, Linux device driver, Go}
        \resumeItem{}{Responsible for integration of different control plane modules.}
        \resumeItem{}{Developed a LTE-type BSR functionality which involved writing kernel module to estimate incoming traffic}
        \resumeItem{}{Built a library to write and read from FPGA registers}
      \resumeItemListEnd

    \resumeSubheading
      {IBM India Pvt. Ltd.}{Bangalore, India}{Software Engineering Intern (Extreme Blue Intern)}
      {May 2017 - Jul 2017}
      \resumeItemListStart
        \resumeItem{}{Implemented a proof of concept that demonstrates Container Management on PowerVM platform by using OpenStack Heat, IBM Spectrum CFC.}

        \resumeItem{}{Developed python automation scripts for easy  installation and deployment of OpenStack with the IBM CFC.}
      \resumeItemListEnd

    \resumeSubheading
      {Great Software Laboratory Pvt. Ltd.}{Pune, India}
      {Software Engineer}{Dec 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{}{Worked on the development of cloud security solution with an objective to secure the workload of user in a cloud-based environment.}
         \resumeItem{}{Designed and developed a user interface using Vaadin GWT for orchestration of OpenStack cloud platform.}
        %  \resumeItem{}{Developed Docker images to support Development and Testing Teams and their pipelines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\vspace{-10pt}
%-----------PROJECTS-----------------
\section{Academic Projects \textit{(more on Github)}}
  \resumeSubHeadingListStart
    \resumeSubItem{CleanG:}{This project involves redesigning the protocol used in core of cellular network with the aim to reduce latency.}
    \resumeSubItem{Implementation of TCP BBR in ns-3}{BBR is a congestion control algorithm proposed by Google for high bandwidth utilization while maintaining the lesser delay. This project also involved the implementation of pre-requisite features (such as pacing, rate sample, etc).}
    \resumeSubItem{Implementation of ECN model for ns-3 TCP stack}{ECN is congestion feedback mechanism widely deployed in the internet. \textit{Status: This model is merged in the mainline of ns-3.}}
    \resumeSubItem{Implementation of TCP DCTCP for ns-3 TCP}{Data Center TCP (DCTCP) is a standard congestion control scheme used to provide high burst tolerance, low latency and high throughput in Data Center Networks (DCNs).\textit{(Status: merged in mainline of ns-3)}}
  \resumeSubHeadingListEnd

%-------PUBLICATIONS------------------  
\section{Publications}
 \resumeSubHeadingListStart
 \resumeItem{}{A. Mohammakhan, K. Ramakrishnan, \textbf{V. Jain}. ``CleanG - Improving the Architecture and Protocols for Future Cellular Networks With NFV" in IEEE/ACM Transactions on Networking. DOI: 10.1109/TNET.2020.3015946}
 
    \resumeItem{}{\textbf{Vivek Jain}, Thomas R. Henderson, and Mohit P. Tahiliani. "Data Center TCP in ns-3: Implementation, Validation and Evaluation." Proceedings of the 2020 Workshop on ns-3. 2020.}
  \resumeItem{}{\textbf{Jain, Vivek}, Viyom Mittal, and Mohit P. Tahiliani. ``Design and implementation of TCP BBR in ns-3." Proceedings of the 10th Workshop on ns-3. 2018.}
  \resumeSubItem{}{Mittal, Viyom, \textbf{Vivek Jain}, and Mohit P. Tahiliani. ``Proportional rate reduction for ns-3 TCP." Proceedings of the 10th Workshop on ns-3. 2018.}
  \resumeSubItem{}{\textbf{Jain, Vivek}, et al. ``Implementation and validation of BLUE and PI queue disciplines in ns-3." Simulation Modelling Practice and Theory 84 (2018): 19-37.}
 \resumeSubHeadingListEnd

%---------------------------------------
% \section{Accomplishments}
%  \resumeSubHeadingListStart
%  \resumeSubItem{}{
%     \textbf{ABC}{XYZ}{LMN}
%     }
%  \resumeSubHeadingListEnd
%-------------------------------------
%---------Teaching/Leadership Experience-------
% \section{Teaching/Leadership Experience}
%  \resumeSubHeadingListStart
%   \resumeSubItem{}{ABC}
%  \resumeSubHeadingListEnd
\end{document}
